%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
%---------------------------------------------------------
\cventry
{Internship in Product Management and D\&D} % Job title
{Bühler AG} % Organization
{Uzwil, Switzerland} % Location
{Feb. 2019 - now} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Market analyse: Benchmarking various product families in Business Component (BC)'s portfolio (i.e. filters, airlocks, pipe diverters) against competitors (on market share, and define optimal manufacturing cost/sales prices in Navigator), to maximise the margin-potential.}
    \item {CAQ: Analyse statistics of installation and customer complains, to identify the problem hotspots for further development opportunities.}
    \item {Support international Sales Dept. with creating/configurating quotations in Navigator, and offering technical clarifications (via standard sheets or in contact with Lifecycle-managers).}
    \item {Managing Design-to-Cost projects, to further reduce manufacturing cost (i.e. diverters).}
    \item {Analyse and improve the filter porfolio on explosion-protection as well as dust emission to satisfy the conformity requirements (ATEX/IEC-Ex, AEx-NFPA68, etc.) and components conformity requirements for food safety (FDA).}
    \item {Create safety analysis (SANA) for the conformity certification of the hopper filter LCCB.}
    \item {Building testing rigs, to test prototypes, specimen of suppliers: EPDM membranes, bearing rings, filter control units.}
    \item {Project management: Collaborate with various production sites (BZAM, BCHI, BBAN, etc.) to standardize the universal motor, and support roll-out airlock (MPSx), cyclone (MGXx) and filter (MVRx) on SIMBA}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
  {Helper} % Job title
  {Swiss Steel AG} % Organization
  {Emmenbrücke, Switzerland} % Location
  {Jul. 2018 - Sep. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Support the annual revision of steel works (reservoirs, hydraulics crane systems).}
      \item {Carry out maintenance work at various parts of the production plant (of construction steel beams)}
    \end{cvitems}
} 

%---------------------------------------------------------
\cventry
{Engineering Internship} % Job title
{Hartmetall Estech AG} % Organization
{Hitzkirch, Switzerland} % Location
{Jul. 2017 - Sep. 2017} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Assist in production hall}
    \item {Prepare quality control probes, before and after sinstering process.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
  {Partime worker} % Job title
  {Zimmermann Technik AG} % Organization
  {Luzern, Switzerland} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Assemble and test magnet coils and various electronics systems/control cabinets.}
    \end{cvitems}
  } 


%---------------------------------------------------------
  \cventry
    {SysAdmin - Operating Manager} % Job title
    {SPOD - VSETH} % Organization
    {Switzerland} % Location
    {Dec. 2013 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Debugging a legacy Ruby on Rails application and developing a new replacement}
        \item {ICT-support for Windows, Mac and Linux systems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Internship} % Job title
    {Reiden Technik AG} % Organization
    {Reiden, Switzerland} % Location
    {Jan. 2013 - Apr. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assemble the combined milling and lathing CNC machines: RX-Serie (RX-10, RX14, and RX-18)}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
